Fig6

### 2020-04-21 analysis/figure-6.Rmd
working on manip figure

getcandidatevsd <- function(whichgenes, whichtissue, whichsex){
  candidates  <- allvsd %>%
    filter(gene %in% whichgenes) %>%
    dplyr::mutate(sextissue = sapply(strsplit(file_name, '_vsd.csv'), "[", 1)) %>%
    dplyr::mutate(sextissue = sapply(strsplit(sextissue, '../results/DEseq2/manip/'), "[", 2)) %>%
    dplyr::mutate(sex = sapply(strsplit(sextissue, '\\_'), "[", 1),
                tissue = sapply(strsplit(sextissue, '\\_'), "[", 2),
                treatment = sapply(strsplit(samples, '\\_'), "[", 4)) %>%
    #dplyr::mutate(treatment = sapply(strsplit(treatment, '.NYNO'), "[", 1))# %>%
   # dplyr::recode(treatment, "m.hatch" = "m.n2", .default = levels(treatment))

     dplyr::mutate(treatment = recode(treatment, "m.hatch" = "m.n2"))%>%

    dplyr::select(sex, tissue, treatment, gene, samples, counts) %>%
    filter(tissue == whichtissue, sex %in% whichsex)  %>%
    drop_na()
  candidates$treatment <- factor(candidates$treatment, levels = alllevels)
  return(candidates)
}

hypvsd <- getcandidatevsd(candidategenes, "hypothalamus", sexlevels)
pitvsd <- getcandidatevsd(candidategenes, "pituitary", sexlevels)
gonvsd <- getcandidatevsd(candidategenes, "gonad", sexlevels)

candidatevsd <- rbind(hypvsd, pitvsd)
candidatevsd <- rbind(candidatevsd, gonvsd)

head(candidatevsd)

levels(candidatevsd$treatment)
```

@@

allDEG$tissue <- factor(allDEG$tissue , levels = tissuelevel)
allDEG$comparison <- factor(allDEG$comparison , levels = comparisonlevels)
allDEG$direction <- factor(allDEG$direction, levels = alllevels)

head(allDEG)

@@

>>>>

head(allvsd)

getcandidatevsd <- function(whichgenes, whichtissue, whichsex){
  candidates  <- allvsd %>%
    filter(gene %in% whichgenes) %>%
    dplyr::mutate(sextissue = sapply(strsplit(file_name, '_vsd.csv'), "[", 1)) %>%
    dplyr::mutate(sextissue = sapply(strsplit(sextissue, '../results/DEseq2/manip/'), "[", 2)) %>%
    dplyr::mutate(sex = sapply(strsplit(sextissue, '\\_'), "[", 1),
                tissue = sapply(strsplit(sextissue, '\\_'), "[", 2),
                treatment = sapply(strsplit(samples, '\\_'), "[", 4)) %>%
    dplyr::mutate(treatment = sapply(strsplit(treatment, '.NYNO'), "[", 1)) %>%
     dplyr::mutate(treatment = recode(treatment, "m.hatch" = "m.n2",
                                                  "extend.hatch" = "m.n2",
                                      "inc.prolong" = "prolong")) %>%

    dplyr::mutate(day = fct_collapse(treatment,
                                     "day 3" = c("inc.d3", "m.inc.d3" ),
                                     "day 9" = c("inc.d9", "m.inc.d9", "m.inc.d8"  ),
                                     "day 17" = c("inc.d17", "m.inc.d17", "prolong"  ),
                                     "hatch" = c("hatch", "m.n2", "extend"  )
                                     )) %>%

    dplyr::mutate(manip = fct_collapse(treatment,
                                       "reference" = charlevels,
                                       "removal" = c("m.inc.d3", "m.inc.d9", "m.inc.d17","m.n2"),
                                       "replacement" = c("m.inc.d8", "prolong", "extend"))) %>%

    dplyr::select(sex, tissue, treatment, day,  manip, gene, samples, counts) %>%
    filter(tissue == whichtissue, sex %in% whichsex)  %>%
    drop_na()
  candidates$treatment <- factor(candidates$treatment, levels = alllevels)
  return(candidates)
}

hypvsd <- getcandidatevsd(candidategenes, "hypothalamus", sexlevels)
pitvsd <- getcandidatevsd(candidategenes, "pituitary", sexlevels)
gonvsd <- getcandidatevsd(candidategenes, "gonad", sexlevels)
candidatevsd <- rbind(hypvsd, pitvsd)
candidatevsd <- rbind(candidatevsd, gonvsd)
head(candidatevsd)
```

@@

allDEG$tissue <- factor(allDEG$tissue , levels = tissuelevel)
allDEG$comparison <- factor(allDEG$comparison , levels = comparisonlevels)
allDEG$direction <- factor(allDEG$direction, levels = alllevels)
head(allDEG)

@@

```{r fig6}
candidatevsd %>%
  filter(gene == "PRL") %>%
  ggplot(aes(y = counts, x = day, color = manip)) +
  geom_boxplot() +
  facet_wrap(tissue~sex, scales = "free") +
  theme(legend.position = "bottom") 
```
